Deeply Virtual Compton Scattering measurement off bound protons

### 2018-12-13 eg6-letters/incoherent/incoherent_prl.tex
update the author list

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the abovementioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi), \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$ \cite{Guidal:2013rya}.

>>>>

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the abovementioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
proportional to the following combination of Compton form factors (CFF) 
$\mathcal{H}$, $\mathcal{E}$, and $\tilde{\mathcal{H}}$ as  
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi), \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$ \cite{Guidal:2013rya}.
